---
output:
  word_document: default
  html_document: default
---
# CHAPTER FOUR
## DATA ANALYSIS/RESULTS/FINDINGS AND DISCUSSIONS
This chapter shall consist of at least the following, among other things:
* **RESULTS/FINDINGS**
The outcome of the research shall be presented and explained in this section. Significant and novel finds shall be identified. The findings shall be stated in and references made to tables, figures or plates in texts where applicable. Details of numerical results shall be given either in the text, in a tabular form or as graphs or any combination of these. The findings may be presented in the descriptive and analytical form.

* **DISCUSSIONS**
This section shall be devoted to giving a comprehensive interpretation of the findings of the research and relating them to published works. Special attention should be given to significant or novel findings



Here is some code and a plot, with a figure caption:
  
## Adding figures

```{r code1, fig.cap='Plot of mpg and hp'}
plot(mtcars$mpg,
     mtcars$hp,
     col = mtcars$wt,
     pch = 19)
```

## Adding Tables


```{r table2}
knitr::kable(
  iris[1:4, 1:5],
  align = 'c',
  caption = 'A table of iris data.',
  col.names = c("Sepal L", "Sepal W", "Petal L", "Petal W", "Species")
)
```
