---
output: word_document
title: "IMPACT OF INCOME INEQUALITY ON POVERTY REDUCTION AND ECONOMIC GROWTH IN NIGERIA(1980-2017)"
author: 
  - "SAMINU ISHAKU"
  - 'SPS/16/MEC/00042'
  - 'BSc Economics'
---
  A Thesis submitted to the Department of Economics, Bayero     University, Kano, in partial fulfillment of the requirements
  for the award of the degree of MASTER
  OF SCIENCE IN ECONOMICS

  August
  2020


---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.align = 'center')
```


# chapter  

## Introduction

This template is based on the `bukthesistemplate` template and modified to meet the requirements of the School of Postgraduate Studies (SPS) of Bayero University, Kano. 

# Chapter

## Literature Review 


# Chapter
##  Methodology 


$$
y_t = \beta_0 + \beta_1X_{1t} + \beta_2X_{2t} + \epsilon_t
$$

Here is some code and a plot, with a figure caption, Figure \@ref(fig:code):
  
```{r code1, fig.cap='Plot of Sepal length and Species length'}
plot(iris$Sepal.Length,
     iris$Sepal.Width,
     col = iris$Species,
     pch = 19)
```


# Chapter
## Data Analysis and Results
Here is some code and a plot, with a figure caption, Figure \@ref(fig:code):
  
## Adding figures

```{r code, fig.cap='Plot of mpg and hp'}
plot(mtcars$mpg,
     mtcars$hp,
     col = mtcars$wt,
     pch = 19)
```

## Adding Tables


```{r table1}
knitr::kable(
  iris[1:4, 1:5],
  align = 'c',
  caption = 'A table of iris data.',
  col.names = c("Sepal L", "Sepal W", "Petal L", "Petal W", "Species")
)
```


# Summary Conclusion and Recommendations 

There are still a few features that would be nice to implement in the future for this template. For instance:

# References

```{r, include=FALSE, eval=FALSE}
knitr::write_bib(c('knitr', 'rmarkdown', 'xaringan'), 'packages.bib')
```

# APPENDIX I 

```{r}
knitr::kable(iris[1:10,1:5], align = 'c')
```
