---
title: "The_BUK_thesis_template"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The_BUK_thesis_template}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


When writing thesis:
* You must meet certain basic requirements

* Format your documents in the required style

* Include the required references style such as APA style

The BUKttr package makes it possible for you to fulfill these requirements by:

* Enabling you to meet the guidelines

* Write and format your document in the required style

* Enabling you to use a pre-populated template

* Making certain basic basic files such as the style available

* Making the references style file available

* Enabling you to start writing your thesis once you are ready

* Making available all the preliminary pages so that you don't miss any

* Enabling you to import your data, analyse data, and get your presentation document all in one piece

# Data wdi_data
* A World Bank dataset name **wdi_data** is included for practicing data manipulation

* The data can be accessed by simply using the following code:

```{r wdi_data}
library(BUKttr)
data("wdi_data")
```

